---
title: "Group 13 CA pollution burden"
author: "Eric Cole and Carleigh Osen"
date: "11/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Attach packages
library(tidyverse)
library(janitor)
library(here)
library(ggplot2)
library(hexbin)
```

```{r, warning = FALSE, message = FALSE}
# Read in the data

ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```

```{r, warning = FALSE, message = FALSE}
# Create basic graph
ggplot(data = ces, aes(x = white_percent,
                        y = ces_3_0_score)) +
  geom_hex(color = "palevioletred2") +
  labs(x = "White Population (% of total population)",
       y = "CalEnviroScreen 3.0 Score") +
  scale_fill_gradient(low = "seagreen1", high = "black") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0.02)) # Adjust caption placement
  
```

**Figure 1:** Comparison of CalEnviroScreen 3.0 Score with the percentage of white population in each census track. Darker hexagons represent a greater number of census tracks that fall under a particular CalEnviroScreen Score and percentage of population that is white.

The overall trend that is observed is that the higher the Caucasian population is in a community, the lower the CalEnviroScreen score is. The data is also skewed to the left.

Citation: 
Eng, Tiffany. CalEnviroScreen 3.0

U.S. Census. 2010. California. 